---
author: JIASHUAI ZHU
output: html_document
---

```{r template-setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Source modules if not already available (standalone mode)
if (!exists("config")) {
  source("../R/config.R")
  source("../R/utils.R")
  source("../R/data_loader.R")
  source("../R/analysis.R")
  config <- get_config()
  df <- load_combined_data(config)
  list_Herbicides <- config$herbicides
  list_colours    <- config$colors
  df_commercial_name_of_herbicide <- load_commercial_names(config)
  farmer <- "Ben Cassidy"
}
```

```{r template-styles, echo=FALSE, results='asis'}
css_path <- file.path(config$project_root, "templates", "styles.css")
if (file.exists(css_path)) {
  cat("<style>\n")
  cat(readLines(css_path), sep = "\n")
  cat("\n</style>\n")
}
```

```{r template-sub-data}
sub_df <- df[df$Farmer_Agronomist == farmer, ]
```

<!-- Outer -->
## Dear __`r farmer`__ {.tabset}

<hr>
 
This report contains information about herbicide resistance of <span style="color:#BF7EBE; font-weight:bold">Clethodim</span>, <span style="color:#FFBF7F; font-weight:bold">Glyphosate</span>, <span style="color:#8BA5F2; font-weight:bold">Sulfometuron</span>, and <span style="color:#FF7F7E; font-weight:bold">Terbuthylazine</span> of your farms.

* The <b>histograms</b> demonstrate the relative situation of your farms compared to your neighbours. The percentile scores indicate how many farms have resistance levels less than or equal to the resistance level of your farms. (For example, 23rd percentile means that 23% of farms we tested have resistance levels less than or equal to the resistance level of your farms; or in other words, your farm is less resistant (better) than 77% of farms we tested.)

* The <b>gradient maps</b> give you a bigger view of the resistance gradient of four herbicides across South-East Australia, and where you farms locate.

 Collection date: November 2018


```{r template-mainBody, results='asis'}

note <- c(
  paste0("\u2022   Clethodim is an acetyl-CoA carboxylase (ACCase) inhibitor, ",
         "which disrupts fatty acid biosynthesis. [Post-emergent] \n\n ",
         "\u2022   Clethodim was applied at a recommended field rate of 120 g ",
         "active ingredient per hectare, 30 days after germination."),
  paste0("\u2022   Glyphosate is a 5-enolpyruvylshikimate-3-phosphate synthase ",
         "(EPSPS) inhibitor, which disrupts the synthesis of aromatic amino acids ",
         "- tyrosine, tryptophan and phenylalanine [Post-emergent] \n\n ",
         "\u2022   Glyphosate was applied at a recommended field rate of 720 g ",
         "active ingredient per hectare, 30 days after germination."),
  paste0("\u2022   Sulfometuron is an acetolactate synthase (ALS) or acetohydroxy ",
         "acid synthase (AHAS) inhibitor, which disrupts the synthesis of branched ",
         "amino acids - valine, leucine and isoleucine. [Pre- and post-emergent] ",
         "\n\n \u2022   Sulfometuron was applied at a recommended field rate of ",
         "400 g active ingredient per hectare, 30 days after germination."),
  paste0("\u2022   Terbuthylazine is a photosystem II (PSII) inhibitor. ",
         "[Post-emergent] \n\n \u2022   Sulfometuron was applied at a recommended ",
         "field rate of 1,050 g active ingredient per hectare, 30 days after germination.")
)

for (i in seq_along(list_Herbicides)) {
  herbicide <- list_Herbicides[i]
  colour    <- list_colours[i]
  survi_col <- paste0(herbicide, "_SURVI")
  ss_col    <- paste0(herbicide, "_sampleSize")

  cat('\n\n### ', herbicide, '\n\n')

  # Herbicide info box
  cat(paste0('\n\n:::: {#box1-', herbicide, ' .textbox} \n\n'))

  commercial_name <- df_commercial_name_of_herbicide$Product.Name[
    which(df_commercial_name_of_herbicide$Active.Ingredient..a.i.. == herbicide)
  ]

  cat('\n\n',
      '<p style="text-align:center; font-size:16px">',
        '<span style=" color:', colour, ';font-weight:bold;font-size: 120%">',
        commercial_name,
        '</span>',
      ' (Product Name)',
      '</p>',
      '\n\n')

  cat("\n\n",
      '<p style="text-align:justify;margin-left:1em;margin-right: 1em">',
      note[i],
      '</p>',
      "\n\n")

  cat('\n\n:::: \n\n')

  # Filter sub-data for this herbicide (safe bracket access)
  sub_df_herb <- sub_df[order(sub_df[[survi_col]], decreasing = FALSE, na.last = NA), ]

  if (nrow(sub_df_herb) != 0) {
    farmers_path_name <- sanitize_name(farmer)

    # Side-by-side plots
    cat('\n\n:::: {.outterdiv style="display: flex;"} \n\n')
    cat('\n\n::: {.imag} \n\n')
    cat('\n\n', '![](', file.path(config$img_dir, farmers_path_name,
        paste0("hist_", herbicide, ".png")), ')', '\n\n')
    cat('\n\n::: \n\n')
    cat('\n\n::: {.imag} \n\n')
    cat('\n\n', '![](', file.path(config$img_dir, farmers_path_name,
        paste0("map_", herbicide, ".png")), ')', '\n\n')
    cat('\n\n::: \n\n')
    cat('\n\n:::: \n\n')

    # Per-farm results box
    cat('\n\n:::: {#box2 .textbox} \n\n')

    all_resistance <- df[[survi_col]]
    all_resistance <- all_resistance[!is.na(all_resistance)]
    sub_resistance <- sub_df_herb[[survi_col]]
    sub_sample_sz  <- sub_df_herb[[ss_col]]

    cat("\n\n", herbicide, " resistance of your farm in ", "\n\n")

    for (j in seq_len(nrow(sub_df_herb))) {
      v_place     <- sub_df_herb$Location[j]
      v_sample_sz <- sub_sample_sz[j]
      v_pct       <- compute_percentile(sub_resistance[j], all_resistance)
      t_pct       <- format_percentile(v_pct)

      if (!is.na(v_pct)) {
        cat(paste0("\n\n", '<ol class="results">',
            '<span style=" color:', colour, ';font-size: 100%">',
                j, '.', ' ', '</span>',
            v_place,
            ' is in a ',
            '<code>', t_pct, ' percentile', '</code>',
            ' situation',
            ';', ' Sample size: ',
            '<code>', v_sample_sz, '</code>',
          '</ol>', "\n\n"))
      }
    }

    cat('\n\n:::: \n\n')
  } else {
    cat('\n\n:::: {.textbox} \n\n')
    cat("\n\n", '<p style="text-align:center; font-size: 18px">',
          "\nSorry, no data available here",
        '</p>', "\n\n")
    cat('\n\n:::: \n\n')
  }
}
```

## {-} 

<hr>

<span style=" color:gray ;font-size: 9px">
Created by JIASHUAI ZHU, JEFFERSON F. PARIL, The Adaptive Evolution Lab</span>
